---
title: "HW6 Solutions"
author: "Alexis Maldonado"
date: "3/8/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## R Markdown
Homework 6 Solutions:
Part1:
- Question 1
```{r}
library(tidyverse)
happy = readRDS("data/HAPPY.rds")
str(happy)
happy = replace(happy, happy == "IAP", NA)
happy = replace(happy, happy == "DK", NA)
happy = replace(happy, happy == "NA", NA)
head(happy)
```
- Question 2 / Question 3
```{r}
happy1 = 
  happy %>% mutate(AGE = replace(AGE, AGE == "89 OR OLDER", 89)) %>% mutate(AGE = as.numeric(AGE),
  HAPPY = as.factor(HAPPY),
  SEX = as.factor(SEX),
  MARITAL = as.factor(MARITAL),
  DEGREE = as.factor(DEGREE)) %>% 
mutate(DEGREE = factor(DEGREE, levels = c("LT HIGH SCHOOL", "HIGH SCHOOL", "JUNIOR COLLEGE","BACHELOR","GRADUATE")))
saveRDS(happy, "HAPPY.rds")
```
Part 2:
```{r}
ggplot(happy1, aes(x = AGE, y = HAPPY, color = as.factor(DEGREE))) +
  geom_point()
```

The graph compares the happiness of people depending on their degree and age. We see that over all in the not too happy the number of high school degree is the highest amount with a lot of lt high school. In the Pretty happy we begin to see less high school and more bachelor degree. Finally in the very Happy we see less high school and lt highschool and more bachelor and some gradute. Because of these we can infer the higher the degree the high your scale of happiness will be. 

